fGFPCA dynamic prediction

### 2023-02-28 f-GFPCA.Rmd
prediction interval

```{r}
# Try on subjects 1-4
in_pred_subj1 <- in_pred_clean(1, mid) %>% 
  left_join(df_true_eta %>% filter(id==1), by = "mid") 
in_pred_subj2 <- in_pred_clean(2, mid) %>% 
  left_join(df_true_eta %>% filter(id==2), by = "mid")
in_pred_subj3 <- in_pred_clean(3, mid) %>% 
  left_join(df_true_eta %>% filter(id==3), by = "mid") 
in_pred_subj4 <- in_pred_clean(4, mid) %>% 
  left_join(df_true_eta %>% filter(id==4), by = "mid") 
```

@@

@@

### Prediction interval

<span style="color:red;"> Questions 3: a lot of problems on this part </span>

Some new updates:

Actually, after going over the full derivation in Leroux2017 paper, I think the preidction interval completely ignored the randomness from fixed effects. In other worlds, prediction intervals are made conditioning on fixed effect coefficients (in our case $\boldsymbol{f_0}$).

>>>>

```{r}
# Try on subjects 1-4
in_pred_subj1 <- in_pred_clean(1, mid) %>% 
  left_join(df_true_eta %>% filter(id==1), by = "mid") 
in_pred_subj2 <- in_pred_clean(2, mid) %>% 
  left_join(df_true_eta %>% filter(id==2), by = "mid")
in_pred_subj3 <- in_pred_clean(3, mid) %>% 
  left_join(df_true_eta %>% filter(id==3), by = "mid") 
in_pred_subj4 <- in_pred_clean(4, mid) %>% 
  left_join(df_true_eta %>% filter(id==4), by = "mid")

# in_pred_subj1 %>% filter(mid >595)
# in_pred_subj2 %>% filter(mid >595)
```

@@

## Prediction interval

Below are some potential methods:

1. Estimate the variance with Empirical Bayes estimators of Gaussian process

- Essentially the same formula as in-sample prediction interval

- This estimate does not change across subject? 
- Also does not change from in- to out-of-sample? 
- Ignore randomness from FPCA estimates (that is, $\boldsymbol{f}_0$, $\boldsymbol{\Gamma}$ and $\sigma_{\epsilon}$).

2. Fisher information matrix

- Based on posterior likelihood
- Standard deviation from this method ended up being very big
- Also does not change from in-sample to out-of-sample, nor across subjects

3. Bootstrap

```{r, warning=FALSE}
source(here("Code/OutSampPredInterv.R"))

# EB
pred_std_eb <- data.frame(mid,
                          t195 = pred_std_eb(fpca_fit, 195),
                          t395 = pred_std_eb(fpca_fit, 395),
                          t595 = pred_std_eb(fpca_fit, 595)) %>%
  pivot_longer(2:4, values_to = "std_eb", names_to = "type") %>%
  mutate(type = factor(type, levels = c("t195", "t395", "t595"),
                       labels=c("Up to 195", "Up to 395", "Up to 595")))

```{r}
pred_std_mle <- data.frame(mid)

for(t in c(195, 395, 595)){
  mle_xi <- out_samp_dyn_pred(df_new = df %>% filter(id==1 & sind_inx<=t) %>%
                           select(-eta_i),fpca_fit = fpca_fit)$score_out
  I_mat <- -gradient(f = llh_div, x = mle_xi, 
                     df_new = df %>% filter(id==1 & sind_inx<=195) %>% select(-eta_i),
                   fpca_fit=fpca_fit)
  std <- sqrt(diag(fpca_fit$efunctions %*% solve(I_mat) %*% t(fpca_fit$efunctions))+fpca_fit$sigma2)

  pred_std_mle <- data.frame(pred_std_mle, std)
}
pred_std_mle <- pred_std_mle %>%  pivot_longer(2:4, values_to = "std_mle", names_to = "type") %>%
  mutate(type = factor(type, levels = c("std", "std.1", "std.2"),
                       labels=c("Up to 195", "Up to 395", "Up to 595")))
```

```{r}
out_pred_subj1 %>%
  left_join(pred_std_eb, by = c("mid", "type")) %>% 
  mutate(eta_upper_eb = eta+std_eb,
         eta_lower_eb = eta-std_eb) %>%
  left_join(pred_std_mle, by = c("mid", "type")) %>% 
  mutate(eta_upper_mle = eta+std_mle,
         eta_lower_mle = eta-std_mle) %>%
  ggplot()+
    geom_line(aes(x=mid, y=true), col="black")+
    geom_line(aes(x=mid, y=eta, col="Estimated"))+
    geom_line(aes(x=mid, y=eta_upper_eb, col="EB"), linetype="dashed")+
    geom_line(aes(x=mid, y=eta_lower_eb, col="EB"), linetype="dashed")+
  geom_line(aes(x=mid, y=eta_upper_mle, col="MLE"), linetype="dashed")+
    geom_line(aes(x=mid, y=eta_lower_mle, col="MLE"), linetype="dashed")+
    facet_wrap(~type)
```

@@
